---
title: "Monitor Central Display - Live Match Data"
author: "Sports Data Pipeline"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(jsonlite)
library(knitr)
library(DT)
```

# Monitor Central JSON Output Example

## Overview
This document shows what the **Monitor Central display data** would look like when implemented with real match data based on your cleaned roadmap structure.

## Live Match Example: Manchester United vs Liverpool

```{json}
{
  "timestamp": "07/02/2025 02:45:30 AM EDT",
  "match_info": {
    "match_id": "1234567",
    "competition_id": "45",
    "competition_name": "Premier League",
    "home_team": "Manchester United",
    "away_team": "Liverpool", 
    "status": "Status ID: 2 (First Half)",
    "live_score": "Man United 1 - 0 Liverpool (42')"
  },
  "corners": {
    "home": 3,
    "away": 5,
    "total": 8
  },
  "odds": {
    "MoneyLine": [
      {
        "time_of_match": "prematch",
        "Home": "2.15",
        "Tie": "3.40",
        "Away": "2.85"
      },
      {
        "time_of_match": "15",
        "Home": "1.95",
        "Tie": "3.60",
        "Away": "3.20"
      },
      {
        "time_of_match": "42",
        "Home": "1.75",
        "Tie": "4.10",
        "Away": "4.50"
      }
    ],
    "Spread": [
      {
        "time_of_match": "prematch",
        "Home": "1.85",
        "Spread": "-0.5",
        "Away": "1.95"
      },
      {
        "time_of_match": "15",
        "Home": "1.90",
        "Spread": "-0.5",
        "Away": "1.90"
      },
      {
        "time_of_match": "42",
        "Home": "1.80",
        "Spread": "-1.0",
        "Away": "2.00"
      }
    ],
    "O/U": [
      {
        "time_of_match": "prematch",
        "Over": "1.90",
        "Total": "2.5",
        "Under": "1.90"
      },
      {
        "time_of_match": "15",
        "Over": "1.85",
        "Total": "2.5",
        "Under": "1.95"
      },
      {
        "time_of_match": "42",
        "Over": "2.10",
        "Total": "3.5",
        "Under": "1.75"
      }
    ],
    "Corners": [
      {
        "time_of_match": "prematch",
        "Over": "1.95",
        "Total": "9.5",
        "Under": "1.85"
      },
      {
        "time_of_match": "15",
        "Over": "1.80",
        "Total": "10.5",
        "Under": "2.00"
      },
      {
        "time_of_match": "42",
        "Over": "2.20",
        "Total": "11.5",
        "Under": "1.65"
      }
    ]
  },
  "environment": {
    "weather": "Clear",
    "pressure": "29.9 inHg",
    "temperature": "64°F",
    "wind": "3.1 mph NE",
    "humidity": "65%"
  }
}
```

## Key Data Fields Breakdown

### 🕐 Timestamp Information
- **NYC Timestamp**: `07/02/2025 02:45:30 AM EDT`
- **Source**: `SOURCE_PRETTY_PRINT_HEADER.nyc_timestamp`

### ⚽ Match Information
```{r echo=FALSE}
match_data <- data.frame(
  Field = c("Match ID", "Competition", "Home Team", "Away Team", "Status", "Live Score"),
  Value = c("1234567", "Premier League", "Manchester United", "Liverpool", 
           "Status ID: 2 (First Half)", "Man United 1 - 0 Liverpool (42')"),
  Source = c("parsed_details.id", "parsed_details.competition_name", 
            "parsed_details.home_team_name", "parsed_details.away_team_name",
            "Formatted status_id", "formatted_live_score")
)

kable(match_data, caption = "Match Information Fields")
```

### 🚩 Corner Statistics
```{r echo=FALSE}
corner_data <- data.frame(
  Team = c("Manchester United (Home)", "Liverpool (Away)", "Total"),
  Corners = c(3, 5, 8),
  Source = c("live_data.parsed_score.home_detailed.corners",
            "live_data.parsed_score.away_detailed.corners", 
            "Calculated: home + away")
)

kable(corner_data, caption = "Corner Statistics")
```

### 💰 Betting Odds Evolution

#### MoneyLine Odds Movement
```{r echo=FALSE}
moneyline_data <- data.frame(
  Time = c("Pre-match", "15 min", "42 min"),
  Home = c("2.15", "1.95", "1.75"),
  Tie = c("3.40", "3.60", "4.10"),
  Away = c("2.85", "3.20", "4.50"),
  Notes = c("Liverpool slightly favored", "Even odds", "Man United heavily favored")
)

kable(moneyline_data, caption = "MoneyLine Odds Evolution")
```

#### Spread Betting
```{r echo=FALSE}
spread_data <- data.frame(
  Time = c("Pre-match", "15 min", "42 min"),
  Home = c("1.85", "1.90", "1.80"),
  Spread = c("-0.5", "-0.5", "-1.0"),
  Away = c("1.95", "1.90", "2.00")
)

kable(spread_data, caption = "Spread Betting Odds")
```

### 🌤️ Environmental Conditions (Converted to US Units)
```{r echo=FALSE}
environment_data <- data.frame(
  Condition = c("Weather", "Pressure", "Temperature", "Wind", "Humidity"),
  Value = c("Clear", "29.9 inHg", "64°F", "3.1 mph NE", "65%"),
  Original = c("Clear", "1013 hPa", "18°C", "5 km/h NE", "65%"),
  Conversion = c("No change", "hPa → inHg", "°C → °F", "km/h → mph", "No change")
)

kable(environment_data, caption = "Environmental Data with US Unit Conversions")
```

## Unit Conversions Applied

### 🌡️ Temperature Conversion
- **Original**: 18°C
- **Converted**: 64°F
- **Formula**: `°F = (°C × 9/5) + 32`

### 🌪️ Wind Speed Conversion  
- **Original**: 5 km/h
- **Converted**: 3.1 mph
- **Formula**: `mph = km/h × 0.621371`

### 📊 Pressure Conversion
- **Original**: 1013 hPa
- **Converted**: 29.9 inHg  
- **Formula**: `inHg = hPa × 0.02953`

## Implementation Notes

1. **Odds Time Tracking**: Shows how betting odds change throughout the match
2. **Corner Calculation**: Automatically sums home and away corners
3. **Status Formatting**: Clear display of match status with ID and description
4. **US Unit System**: All environmental data converted to US standard units
5. **Real-time Updates**: Data structure supports live updating every 60 seconds

## Data Pipeline Integration

This JSON structure is the final output of your 4-stage pipeline:
1. **all_api.py** → Raw data collection
2. **merge.py** → Data enrichment  
3. **pretty_print.py** → Data cleaning
4. **monitor_central.py** → Final display formatting

**Perfect for**: Dashboards, mobile apps, web interfaces, and monitoring systems!